\documentclass[letterpaper,10pt,titlepage]{article}

\usepackage{color}
\usepackage{enumitem}


%random comment

\usepackage{hyperref}

\def\name{Jack Neff}

%pull in the necessary preamble matter for pygments output

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {CS461 Capstone},
  pdftitle = {CS 461 Technical Review}
  pdfsubject = {Rough draft for capstone fall 2017},
  pdfpagemode = UseNone
}

\begin{document}
\begin{center}
\thispagestyle{empty}
\parskip=14pt%
\vspace*{3\parskip}%

\Huge Green Smart Gardening System Design

\large Jack Neff

\Large Oregon State University

\large CS 461, Fall 2017, TR 12pm

\large Turned in: 11/21/2017

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

\small Abstract

\small 

\clearpage

\end{center}

\section{Introduction}
	
My group is tasked with building a Green Smart Gardening System that automates gardening and farming processes. A scaled up version of our design would tend vineyards or orchards. The hardware used will consist of a sensor array, a solar panel, and a connected microcontroller, as well as a remote desktop computer connected to the microcontroller via wi-fi. 

I am in charge of the display and storage of data, as well as the implementation of our application as a web-based UI. Our project involves collecting environmental data from a garden with a microcontroller and then displaying this data to users. For starters we need an application stack with an HTTP server, a database, and a PHP interpreter. We also need to select the correct database storage engine for our application, to store data in a way that can be graphically displayed. Finally we need a graphics application that will allow us to display our data in clear and interesting ways. Users will login to our web application where they can view interesting and colorful displays of data sorted in our database that came from wi-fi transmissions from a microcontroller. 


\section{Server Database Interpreter Stack}

\section{Graphical Display}


\textbf{Selection: D3js}
\clearpage

\begin{thebibliography}{9}

\bibitem{AlternativeTo}AlternativeTo. (2017). WampServer Alternatives and Similar Software - AlternativeTo.net. [online] Available at: https://alternativeto.net/software/wamp/ [Accessed 21 Nov. 2017].

\bibitem{Bitnami}Bitnami.com. (2017). LAMP. [online] Available at: https://bitnami.com/stack/lamp [Accessed 18 Nov. 2017].

\bibitem{Github}Koch, J. (2017). WPN-XM/WPN-XM. [online] GitHub. Available at: https://github.com/WPN-XM/WPN-XM/wiki [Accessed 21 Nov. 2017].

\bibitem{NGINX}Garrett, O. (2017). NGINX vs. Apache: Our View of a Decade-Old Question. [online] NGINX. Available at: https://www.nginx.com/blog/nginx-vs-apache-our-view/ [Accessed 21 Nov. 2017].

\bibitem{panoply}Sarig, M. (2017). MariaDB vs MySQL. A Comparative. [online] Blog.panoply.io. Available at: http://blog.panoply.io/a-comparative-vmariadb-vs-mysql [Accessed 21 Nov. 2017].

\bibitem{mysql} Dev.mysql.com. (2017). MySQL :: MySQL NDB Cluster 7.5 :: 3.5.1 Differences Between the NDB and InnoDB Storage Engines. [online] Available at: https://dev.mysql.com/doc/mysql-cluster-excerpt/5.7/en/mysql-cluster-ndb-innodb-engines.html [Accessed 21 Nov. 2017].

\bibitem{Wikipedia}En.wikipedia.org. (2017). Comparison of MySQL database engines. [online] Available at: https://en.wikipedia.org/wiki/Comparison\_of\_MySQL\_database\_engines [Accessed 17 Nov. 2017].

\bibitem{Gephi}Gephi.org. (2017). Features. [online] Available at: https://gephi.org/features/ [Accessed 21 Nov. 2017].

\bibitem{B. Sullins}Sullins, B. (2017). Tableau vs D3 - Which one should I use? - Ben Sullins | Data Geek. [online] Ben Sullins | Data Geek. Available at: https://bensullins.com/tableau-vs-d3-one-use/ [Accessed 18 Nov. 2017].

\end{thebibliography}

\end{document}
